Symmetric Peer-to-Peer Applications

### 2022-08-19 tpd-22.tex
...

An antagonistic approach to deterministic reactions to events is to model the
application data structures with conflict-free replicated data types
(CRDTs)~\cite{TODO}.
CRDTs are designed in such a way that all operations are commutative, so that
the order in which they are applied does not affect the final outcome.
%
As detailed in Figure~\ref{fig.algos}, peers can communicate operations
directly to each other with no central authority.
Also, since operations need not to be ordered, they can be applied at the
very first moment they are generated or received, even if the peers are
offline.
%
Since operations must be commutative, it is not possible to timestamp them
in a global shared clock.
Hence, there is no notion of a timeline with peers going through bit-identical
steps, but they do eventually reach the same state.
%
On the one hand, the main advantage of CRDTs is they support the concept of
local-first software~\cite{TODO}, since they work offline.
On the other hand, they provide very restrictive APIs (the CRDTs themselves),
and do not support real-time consensus among peers.
%
Automerge~\cite{TODO} along with its accompanying Hypermerge peer-to-peer
infrastructure is an example of an implementation of this approach.

In this work, we try to .

>>>>

An antagonistic approach to deterministic reactions to events is to model the
application data structures with conflict-free replicated data types
(CRDTs)~\cite{TODO}.
CRDTs are designed in such a way that all operations are commutative, so that
the order in which they are applied does not affect the final outcome.
%
As detailed in Figure~\ref{fig.algos}, peers can communicate operations
directly to each other with no central authority.
Also, since operations need not to be ordered, they can be applied at the
very first moment they are generated or received, even if the peers are
offline.
%
Since operations must be commutative, it is not possible to timestamp them
in a global shared clock.
Hence, there is no notion of a timeline with peers going through bit-identical
steps, but they do eventually reach the same state.
%
On the one hand, the main advantage of CRDTs is they support the concept of
local-first software~\cite{TODO}, since they work offline.
On the other hand, they provide very restrictive APIs (the CRDTs themselves),
and do not support real-time consensus among peers.
%
As indicated in Figure~\ref{fig.table}, CRDTs work on decentralized networks,
in which nodes advance independently, and in which operations can be applied
immediately, even while offline.
%
Automerge~\cite{TODO} along with its accompanying Hypermerge peer-to-peer
infrastructure is an example of an implementation of this approach.

In this work, our goal is to support peer-to-peer real-time symmetric
execution, while still tolerating offline and out-of-order event generation.
%
As detailed in Figure~\ref{fig.algos}, peers have their own timeline and can
communicate events directly to each other.
Events are delayed to be able to reach other peers in time.
In the case deadlines are missed, the peer rolls back in time and simulates
the execution in fast forward until it reaches real time again.

, in which nodes advance independently, and in which event outcomes
depend on the originating node to be online.

we try to .
